---
title: "Science Week Talk"
author: "Hamed Bastan-Hagh"
date: '14 March 2023'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#002060",
  inverse_header_color = "#FFFFFF",
  link_color = "#FF69B4"
)
```

class: middle, inverse

# Data Scientist

???

Raise your hand if you know what a data scientist does.

---

.pull-left[
## Data
### Information about the world, people, the universe ...
]

.pull-right[
## Scientist
### Understand and explain how the world works.
]

---

layout: false

class: middle, inverse

## A data scientist uses data to understand and explain how the world works.

---

class: middle, inverse, center

## Data Scientist $\approx$ Statistician

---

class: middle, center

![](https://upload.wikimedia.org/wikipedia/commons/b/b8/YouTube_Logo_2017.svg)

---

## Start with a question ...

--

## ... Turn that into a maths question ...

--

## ... Put data into the maths question ...

--

## ... Translate back to the original question.

---

## 1. Maths
## 2. Programming
## 3. Translating real-world problems into maths (and back again)
